%!TEX root = ../article.tex
\subsection{Projection View}
To help users obtain an overview of case clusters and outliers (\textbf{T5}), we design the Projection View (Fig.\ref{fig:teaser}E) which supports various interactions such as zooming and brushing to allow users to select a subset of data for further examination (\textbf{T7}). 

In the Projection View, each circle represents a individual case. There are many multi-dimensional reduction methods such as MDS and PCA; we select t-SNE as it can strongly repel dissimilar points and show clusters clearly.
\QM{Given an individual case, we flatten the cluster importance at all timestamps (discussed in Sec.\ref{section:feature_importance}) to 1-dimensional as the t-SNE embedding vector.}
Thus, the positions of the circles reflect the similarity of their cluster importance.

When multiple data subsets are selected, we use a categorical color scheme to fill the circles so that the data sequences from the same data subset will have the same color in both components.
Users can brush to select data sequences for detailed examination in the Sequence View.

One major consideration in developing the Projection View is the scalability problem.
When the number of circles is large, the circles may overlap with each other, and the Projection View can be cluttered.
We adopt a node overlap removal algorithm for the similarity projection and support panning and zooming to allow users to explore a data subset.

Furthermore, to improve the flexibility of the case selection, we add a two-scale timeline (Fig.\ref{fig:teaser}E top) to show the target feature trend, enabling user filtering of the  cases by time, and a feature selection component (Fig.\ref{fig:teaser}E right) to filter the cases by feature value.  

