\subsection{Case exploration}

In Hong Kong, air quality always shows seasonal patterns such as the ``large winter-summer contrasts in $PM_{2.5}$ mass" due to the Asiatic monsoon~\cite{louie2005seasonal}. We conduct this case study to understand the model behavior in different seasons.  

\subsubsection{Overview of the model behavior across seasons}

The Projection View allows users to select individual cases according to different times by brushing on the timeline (Fig.~\ref{fig:teaser}E) and provides an overview of all cases (\textbf{T5}).
We first choose the GRU-Dense model and target feature of $PM_{2.5}$.
We gradually select the time ranges to roughly filter the cases in winter, spring, summer, and fall. 
The unfiltered sequences are colored in light grey to highlight the selected cases as shown in  Fig.~\ref{fig:seasonal_feature}. 
We found that the fall and winter sequences are clustered at the left-bottom part of the whole figure (Fig.~\ref{fig:seasonal_feature}A,D). 
The sequences in summer gather at the right-top part (Fig. \ref{fig:seasonal_feature}C), while the sequences in spring are distributed in different locations compared with the other three seasons (Fig.\ref{fig:seasonal_feature}B).
Even though some outliers exist in the Projection View as shown in Fig.~\ref{fig:seasonal_feature}A$_1$,C$_1$, we can find the model can capture the complex seasonal features in data. 

\subsubsection{Explore the model behavior in winter}

Furthermore, we notice that several sequences indicate the target location has a serious $PM_{2.5}$ pollutant in winter. 
In the Projection View, we first select the time range of January 2018 (Fig.~\ref{fig:winter_exploration}A) to highlight all the cases in this time range (Fig. \ref{fig:winter_exploration}B). 
We notice there are many cases are colored in dark red, which indicates these cases suffer a heavy $PM_{2.5}$ pollutant (Fig.~\ref{fig:winter_exploration}C1).
We select these sequences to explore their feature importance distributions and rankings.
The top ten important features are \textit{\color{WINDColor}{Wind Speed}}, $\color{PM25Color}{PM_{2.5}}$ and $\color{PM10Color}{PM_{10}}$.
The selected sequences also appear in the Individual Views; all these sequences form one stack, and we choose one of them as an example as shown in Fig.~\ref{fig:winter_exploration}E$_1$. 
In the Cluster Importance Chart, cluster 3, 6, and 7 show great influence in the forecast. 
These corresponding feature clusters are shown in Fig.~\ref{fig:winter_exploration}E$_3$, which presents the clusters of $PM_x$ and \textit{Wind Speed} respectively. 
The above exploration further indicates that the most important features in the forecasting are about $\color{PM25Color}{PM_{2.5}}$, $\color{PM10Color}{PM_{10}}$, and \textit{\color{WINDColor}{Wind Speed}}. 

The domain expert states: ``During winter, strong radiative cooling over the continent creates a high-pressure anticyclone that drives cold, dry polar air from the continent into the surrounding oceanic areas, resulting in weak to moderate northeasterly winds or strong northerly winds" \cite{louie2005seasonal, murakami1979winter}. 
The weak to moderate wind is able to bring the air pollutant from Pearl River Delta region in China, which is a highly populated region and has a lot of heavy industry \cite{cao2003characteristics}.
Thus, the major factors that mostly influence Hong Kong's air quality in winter are the air pollutants and the wind.
Specifically, the $PM_{2.5}$ and $PM_{10}$ from the north and east affects the prediction results the most. 

We are also interested in how different models behave between the high-pollutant and low-pollutant sequences in the winter. 
We select individual cases with low $PM_{2.5}$ from the Projection View as Fig.~\ref{fig:winter_exploration}C$_2$ shows, and two stacks if individual cases appear in the Individual View. 
By observing the representative case (Fig.\ref{fig:winter_exploration}E$_2$), we find a cluster which is very important at the last timestamp in the Cluster Importance Chart (Fig.~\ref{fig:winter_exploration}E$_4$), which indicates nearby $PM_{2.5}$ and $PM_{10}$. 
Both the Top Feature List (Fig.~\ref{fig:winter_exploration}E$_5$) and the Cluster Importance Chart show that the features of recent time steps are very important for the forecast, which is different from the heavy pollution sequences (Fig.~\ref{fig:winter_exploration}E$_6$). 
We guess that for the low air pollutant (target feature) cases, only recent important features are leveraged by the model. 

